Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-09-09 ms.tex
updates to FPA temp change plot and text.

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{allan_var_removelinear_False_darkBaseline.pdf}
\caption{The noise in a dark exposure scales with 1/$\sqrt{N}$ for $N$ exposures, as would be expected for white noise.
Here, we have assumed an illumination of 3.7$\times10^8$ DN to convert the noise in DN to a relevant ppm for illuminated data.
While 1/f noise substantially increases the noise over the assumption that each pixel's read noise is statistically independent, each integration is statistically independent.
}\label{fig:darkBaselineAllan}
\end{figure*}

@@

\clearpage
\subsection{FPA temperature change}
\begin{figure*}
{\gridline{\fig{individual_azlab05_baseline_tchange.pdf}{0.99\textwidth}{}}}
\caption{Time series during an adjustment to the FPA set point.}\label{fig:indTSeriesAfterLamp}
\end{figure*}

@@

>>>>

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{allan_var_removelinear_False_darkBaseline.pdf}
\caption{The noise in a dark exposure scales with 1/$\sqrt{N}$ for $N$ exposures, as would be expected for white noise.
Here, we have assumed an illumination of 3.7$\times10^8$ DN to convert the noise in DN to a relevant ppm for illuminated data.
While 1/f noise substantially increases the noise over the assumption that each \textit{pixel's} read noise is statistically independent, each \textit{integration} is statistically independent.
}\label{fig:darkBaselineAllan}
\end{figure*}

@@

\clearpage
\subsection{FPA temperature change}
We purposely adjusted the focal plane array temperature set point mid-way through a long exposure to test how the detectors' temperatures will affect their response to light.
As can be seen in Figure \ref{fig:indTSeriesAfterLamp} (bottom panel) the Lakeshore temperature controlling a baseplate where the largest thermal mass sits is constant to within 3 mK.
The FPA temperature is adjusted upward by 300 mK about 75 minutes into the test and held at this higher value.
The change in temperature results in a 0.1\% increase in flux (ie. 1000 ppm).
In terms of slopes, this resulted in a change of 2.3 DN/s/px for detector 487 and 3.6 DN/s/px for detector 489.
For the integration times of 10.77 seconds, this amounts to 25 to 39 DN accumulated within an integration.
This is lower than the value of 80 DN for a 100 mK change in \citet{hall2005jwstArrays}, likely because it is calculated over the slope of an image rather than the absolute counts.

The reaction to FPA changes in temperature is likely a fractional effect rather than an absolute number of DN.
This is because both detectors change by about 0.10\% even though their relative peak counts were 25,000 DN/px and 39,000 DN/px for detectors 487 and 489.

In flight, the FPA is expected to be stable to about 1 mK.
If we take the observed flux change (1000 ppm per 300 mK), the fractional change will be about 3 ppm. We therefore expect detector temperature fluctuations to be a relatively small part of the time series error budget.

\begin{figure*}
{\gridline{\fig{individual_azlab05_baseline_tchange.pdf}{0.99\textwidth}{}}}
\caption{Time series during an adjustment to the FPA set point.}\label{fig:indTSeriesAfterLamp}
\end{figure*}

@@

\section{Conclusions}

\begin{itemize}
	\item \textbf{1/f Noise:} This is a major contributor to the noise. It is important to subtract along the fast-read (horizontal) direction to reduce the correlated noise. Fortunately, 1/f noise appears to average like $1/\sqrt{N} $
	\item \textbf{Subpixel Sensitivity:}
	\item \textbf{Charge Trapping/Persistence/HST Ram-up:} Expected to be much smaller than HST and timescales are much faster. Long timescale traps contribute less then 1e-/DN/px so they are less problematic.
\end{itemize}
